Bioverse: Origins of Life

### 2024-09-07 src/tex/ms.tex
remove duplicate text

A real exoplanet survey will be subject to observational biases, sample selection effects, and the underlying demographics of the planet sample.
To assess the information gain of a realistic exoplanet survey, we employed Bioverse~\citep{Bixel2021,Hardegree-Ullman2023,Schlecker2024,Hardegree-Ullman2024}, a framework that integrates multiple components including statistically realistic simulations of exoplanet populations, a survey simulation module, and a hypothesis testing module to evaluate the statistical power of different observational strategies.
The general approach is as follows:
After defining a population of synthetic exoplanets, we simulate the detection and characterization of these exoplanets with a hypothetical survey, taking into account the survey’s sensitivity, target selection, and observational biases.
Then we evaluate the likelihood that a given survey would detect a specified demographic trend in the exoplanet population and estimate the precision with which the survey could constrain the parameters of that trend.
A common definition of the null hypothesis $H_0$, which is also applied here, is that there is no relationship between the independent variable (here: maximum \gls{NUV} flux) and the dependent variable (here: biosignature occurrence).
The alternative hypothesis $H_1$ proposes a specific relationship between the independent and dependent variables.
To determine the diagnostic capability of a given survey, Bioverse runs multiple iterations of the simulated survey and calculates the fraction of realizations that successfully reject the null hypothesis.
We use this metric, known as the statistical power, to quantify the potential information content of the survey, identify critical design trades, and find strategies that maximize the survey’s scientific return.

@@

\subsection{Exoplanet survey simulations with Bioverse}
A real exoplanet survey will be subject to observational biases, sample selection effects, and the underlying demographics of the planet sample.
To assess the information gain of a realistic exoplanet survey, we employed Bioverse~\citep{Bixel2021}, a framework that integrates multiple components including statistically realistic simulations of exoplanet populations, a survey simulation module, and a hypothesis testing module to evaluate the statistical power of different observational strategies.
The general approach is as follows:
\begin{enumerate}
\item \textbf{Exoplanet population synthesis:} We populate the Gaia Catalogue of Nearby Stars~\citep{Smart2021} with synthetic exoplanets whose orbital parameters and planetary properties reflect our current understanding of exoplanet demographics~\citep{Bergsten2022}.
    \item \textbf{Survey simulation:} We simulate the detection and characterization of these exoplanets with a hypothetical survey, taking into account the survey's sensitivity, target selection, and observational biases.
To model the sensitivity of the information gain of a proposed mission to sample selection and survey strategy, we conduct survey simulations with Bioverse using different sample sizes and survey strategies.
    \item \textbf{Hypothesis testing:} We evaluate the likelihood that a given survey would detect a specified demographic trend in the exoplanet population and estimate the precision with which the survey could constrain the parameters of that trend.
    A common definition of the null hypothesis $H_0$, which is also applied here, is that there is no relationship between the independent variable (here: maximum NUV flux) and the dependent variable (here: biosignature occurrence).
    The alternative hypothesis $H_1$ proposes a specific relationship between the independent and dependent variables.
    Bioverse offers either Bayesian model comparison or non-parametric tests to evaluate the evidence for or against the null hypothesis.

>>>>

A real exoplanet survey will be subject to observational biases, sample selection effects, and the underlying demographics of the planet sample.
To assess the information gain of a realistic exoplanet survey, we employed Bioverse~\citep{Bixel2021,Hardegree-Ullman2023,Schlecker2024,Hardegree-Ullman2024}, a framework that integrates multiple components including statistically realistic simulations of exoplanet populations, a survey simulation module, and a hypothesis testing module to evaluate the statistical power of different observational strategies.

@@

\subsection{Exoplanet survey simulations with Bioverse}
To assess the diagnostic power of realistic exoplanet surveys, we employed our survey simulator and hypothesis testing framework Bioverse~\citep{Bixel2021}
The general approach is as follows:
\begin{enumerate}
\item \textbf{Exoplanet population synthesis:} We populate the Gaia Catalogue of Nearby Stars~\citep{Smart2021} with synthetic exoplanets whose orbital parameters and planetary properties reflect our current understanding of exoplanet demographics~\citep{Bergsten2022}.
    \item \textbf{Survey simulation:} We simulate the detection and characterization of these exoplanets with a hypothetical survey, taking into account the survey's sensitivity, target selection, and observational biases.
To model the sensitivity of the information gain of a proposed mission to sample selection and survey strategy, we conduct survey simulations with Bioverse using different sample sizes and survey strategies.
    \item \textbf{Hypothesis testing:} We evaluate the likelihood that a given survey would detect a specified demographic trend in the exoplanet population and estimate the precision with which the survey could constrain the parameters of that trend.
    A common definition of the null hypothesis $H_0$, which is also applied here, is that there is no relationship between the independent variable (here: maximum NUV flux) and the dependent variable (here: biosignature occurrence).
    The alternative hypothesis $H_1$ proposes a specific relationship between the independent and dependent variables.
    Bioverse offers either Bayesian model comparison or non-parametric tests to evaluate the evidence for or against the null hypothesis.
